Evolution of \\ ice sheet geometry \\ using Stokes dynamics

### 2021-06-21 talk/talk.tex
More.

\bigskip
\begin{itemize}
\item \alert{smoothness suggests $s$ is better for multigrid}
    \begin{itemize}
    \item \emph{corollary}. do not put ``fake ice'' where $s=b$
    \item only solve for ice velocity where there is ice!
    \end{itemize}
\end{itemize}
\end{frame}

@@

\item this strategy gives an $O(m\log m)$ solver for the Laplacian obstacle problem (Tai, 2003)
    \begin{itemize}
    \item \only<1>{a multilevel VI strategy is the only hope for (near) optimality}\only<2>{\alert{a multilevel VI strategy is the only hope for (near) optimality}}
    \end{itemize}
\item for IGP:
    \begin{itemize}
    \item for nonlinear VI, need additional FAS strategy {\Large\strut} \only<2>{{\color{ForestGreen} \, {\Large $\checkmark$}}}
    \item each residual is nonlocal and expensive {\Large\strut} \only<2>{{\color{ForestGreen} \, {\Large $\checkmark$}}}
    \item<2> {\color{ForestGreen} strategy implemented}
    \end{itemize}
\end{itemize}
\end{frame}

>>>>

\bigskip
\begin{itemize}
\item \alert{smoothness suggests $s$ is better for multigrid}
    \begin{itemize}
    \item but \emph{do not} put ``fake ice'' where $s=b$; only solve for ice velocity where there is ice!
    \end{itemize}
\end{itemize}
\end{frame}

@@

\item this strategy gives an $O(m\log m)$ solver for the Laplacian obstacle problem (Tai, 2003)
    \begin{itemize}
    \item \alert{a multilevel VI strategy is the only hope for (near) optimality}
    \end{itemize}
\item for IGP:
    \begin{itemize}
    \item for nonlinear VI, need additional FAS strategy {\Large\strut} \only<2>{{\color{ForestGreen} \, {\Large $\checkmark$}}}
    \item each residual is nonlocal and expensive {\Large\strut} \only<2>{{\color{ForestGreen} \, {\Large $\checkmark$}}}
    \item<2> {\color{ForestGreen} strategy implemented}
    \end{itemize}
\end{itemize}
\end{frame}
